Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-22 NEUROC/sec4-experiments.tex

\subsection{Inference Time Breakdown Analysis}
% 该部分

%

@@

>>>>

% added by wangyunpan, 2020-12-22 ----start----
\paragraph{Inference Time Breakdown Analysis}
We conducted the same experiments in the inference stage as above.
%
The results of layer level experiment, step Level in edge Calculation experiment and operator Level experiment were in general consistent with those in the Training stage.
%
The performance bottleneck analysis in the Training stage can also be applied to the inference stage.
% added by wangyunpan, 2020-12-22 ----end----

@@

% added by wangyunpan, 2020-12-22 ----start----
\paragraph{Inference Stage Memory Usage Analysis}

% 不同点: phase
\begin{figure}[H]
    \centering
    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_usage_stage_amp.pdf}
    \caption{Memory usage of each phase during the GNN training. Dataset: \texttt{amp}.}
    \label{fig:exp_inference_full_memory_usage_stage_amp}
\end{figure}

% 不同点： 膨胀比例
\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\columnwidth]{figs/experiments/exp_inference_full_memory_expansion_ratio.pdf}
    \caption{Memory expansion ratios of typical GNNs.}
    \label{fig:exp_inference_full_memory_expansion_ratio}
\end{figure}

% 不同点: input feature dims
\begin{figure}[H]
    \centering
    \includegraphics[height=5cm]{figs/experiments/exp_inference_full_memory_expansion_ratio_input_feature_dimension_com-amazon_expansion_ratio.pdf}
    \caption{Memory expansion ratio under different dimensions of input feature vectors. Dataset: \texttt{cam}.}
    \label{fig:exp_inference_full_memory_expension_ratio_input_feature_dimension}
\end{figure}

For the inference stage, we did the same experiment as above. The experimental results were as follows:
%
\figurename~\ref{fig:exp_inference_full_memory_usage_stage_amp} shows the peak memory usage of each phase during inference stage.  
%
Compared with the results of training stage in \figurename~\ref{fig:exp_memory_usage_stage_amp}, the peak memory usage of inference stage was significantly lower.
%
This was because the inference stage didn't require backward propagation and the peak memory was only determined by the temporary variables generated during the computation.
%

\figurename~\ref{fig:exp_inference_full_memory_expansion_ratio} compares MER of different GNNs on inference stage. 
%
We found that the performance of GNNs on all datasets was consistent with the training stage (\figurename~\ref{fig:exp_memory_expansion_ratio}). 
%

% added by wangyunpan, 2020-12-22 ----end----
